\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)

### 2021-06-24 authors_responses/first_tac_rejection/authors_response.tex
Lots of types fixed in main manuscript Removed the requirements of the system model - measurement vec/mat now have unknown dimension and have been written with 0...0 for the sections where this is the case - author's responses have been changed to reflect this Results sections updated to point out that the plotted track is only a sample track

We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out. Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision. For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal. We will also consider some of the denser cryptographic definitions presented for an alternative submission elsewhere.

@@

Thank you for pointing this out. This was due to an error in notation in a previous section which gave incorrect timestep subscripts in the EKF prediction equations. This has now been fixed and results in $\mat{F}_k$ being the correct notation in the pseudocode section.

@@

The method proposed achieves the desired security properties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step. With this method, using the EIF is crucial for reducing participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties. It may be possible to rearrange a particle filter to suit some other type of encryption scheme, but to the best of our knowledge, this does not yet exist.

During only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter, but we have decided to use the prediction equations of the EKF for simplicity and consistency with the presented update step.

@@

The linear combination aggregation scheme is only used to encrypt the required communication during the computation of the EIF update step. Ideally, the encryption does not affect the proposed filter in any way, but in practice, minor discrepancies are introduced with the quantisation of floating-point numbers. The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF are introduced. The system model given in ($2$) is unaffected by both encryption and measurement model modification, in that both the proposed filter and the standard EIF assume the state follows these dynamics exactly.

@@

Thank you for pointing this out. It is correct that the Gaussianity of additive system noise is not required by either the standard EIF or our approach and has now been removed from the manuscript.

@@

Estimating the second moment of the system noise, $\mat{Q}$, is a standard requirement when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag). This can be done in various ways specific to the system being modelled and is beyond the scope of this work. As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have used the EKF equations for state prediction, computing it would be necessary.

@@

We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer. To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly. The computational performance is more difficult to compare. Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript). Future work is being done on a similarly modified EIF which can used a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.

>>>>

We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out. As cryptography is becoming more prevalent in the context of control and estimation literature, existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision. For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal. We will also consider some of the denser cryptographic definitions presented for an alternative submission elsewhere.

@@

Thank you for pointing this out. This was due to an error in notation from a previous section which gave incorrect timestep subscripts to the EKF prediction equations. The revised manuscript no longer imposes using the EKF for the prediction step of the filter and these equations have been removed.

@@

The method proposed achieves the desired security properties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step. With this method, using the EIF is crucial for reformulating participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties. It may be possible to rearrange a particle filter to suit some other type of encryption scheme, but to the best of our knowledge, this does not yet exist.

However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter. We have now relaxed the requirements of the system model and no specify the prediction equations of EKF specifically.

@@

The linear combination aggregation scheme does not reflect or affect the dynamics of the system model given in ($2$). The scheme is only used to encrypt the required communication during the computation of the EIF update step. The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF update are introduced. As above, we have removed the restrictions on the system model and hope that this makes its role in the presented filter clearer.

@@

Thank you for pointing this out. It is correct that the Gaussianity of the system noise was not required by our approach, nor was it required for the locally computed prediction step of the filter. This assumption is among the restrictions on the system model which have now been removed from the manuscript.

@@

As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearlising filter for the prediction step of the algorithm. However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag) and has been computed when evaluating the proposed filter through simulation. This can be done in various ways specific to the system being modelled and is beyond the scope of this work.

@@

We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer. To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly. The computational performance is more difficult to compare. Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript). Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
